\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-21 chapters/1_intro.tex
Update figs; squeeze text

\section{Introduction}
\UPDATE{\today,\currenttime} -  In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g. image classification, object recognition, image parsing
% to model many types of re- lations and processes in physical, biological, social and information systems
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even a supervision in terms of seeds (e.g. seeded watershed or random walker).  
%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters. Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

@@

In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e. mutual exclusion between clusters. We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.9\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ \textbf{Left:} raw data from the CREMI 2016 neuron-segmentation challenge and short- / long-range predictions of a CNN. \textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework. The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). When signed graphs are used, the final clustering / instance segmentation is shown in (b). We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

\section{Introduction}
In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g. image classification, object recognition, image parsing
% to model many types of re- lations and processes in physical, biological, social and information systems
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even a supervision in terms of seeds (e.g. seeded watershed or random walker).  
%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters. Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

@@

In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. %, i.e. mutual exclusion between clusters. 
We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ \textbf{Left:} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{Middle:} Short- and long-range predictions of our UNet model. \textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework. The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). The final clustering / instance segmentation is shown in (b). We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-21 chapters/2_rel_work.tex
Update figs; squeeze text

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and \UPDATE{biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
% the introduction of new architectures lead to a much more refined boundary detection. 
% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
% Subsequent postprocessing and superpixel-merging outputs final instances. 
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
% \SOURCE{SSHMT} Check Funke proposals

>>>>

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
% the introduction of new architectures lead to a much more refined boundary detection. 
% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
% Subsequent postprocessing and superpixel-merging outputs final instances. 
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
% \SOURCE{SSHMT} Check Funke proposals

### 2019-05-21 chapters/5_experiments_cityscapes.tex
Update figs; squeeze text

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
For our experiments, we used the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}. See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.

Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage. MultiStepHAC requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.

\begin{figure}[t]
\centering
\begin{minipage}[T]{0.59\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores on the cityscapes validation set achieved by the tested pipelines}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to introduce more false region-splits, like \emph{Abs. Max.}, or false region-merge, like \emph{Sum}. In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes all other tested linkage. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by \cite{liu2018affinity}, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.6\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the cityscapes validation set achieved by the tested pipelines.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=0.95\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

### 2019-05-21 chapters/5_experiments_intro.tex
Update figs; squeeze text

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
First, we present how we predicted signed edge weights with a CNN. Then we introduce the CREMI challenge and our tested methods in Sec. \ref{sec:cremi_challenge} and finally we present our results in Sec. \ref{sec:results}.

% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. 
Thus, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

>>>>

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
%First, we present how we predicted signed edge weights with a CNN. Then we introduce the CREMI challenge and our tested methods in Sec. \ref{sec:cremi_challenge} and finally we present our results in Sec. \ref{sec:results}.

% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to direct neighboring pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.
